\documentclass[11pt]{res} % default is 10 pt
\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
\usepackage{newcent}   % uses new century schoolbook postscript font 
\setlength{\textheight}{9.5in} % increase text height to fit resume on 1 page
\newsectionwidth{0pt}  % So the text is not indented under section headings

\usepackage{color}
\usepackage{setspace}
\usepackage{fontawesome}
\usepackage[hidelinks]{hyperref}
\usepackage{makecell}

% lastpage does not work with hyperref :-(
%\usepackage{lastpage}
\usepackage{fancyhdr}
\pagestyle{fancy}
% My pagestyle is fancy because I want to put footers, but I remove everything else from this fancy style
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}

% Redefinition, symbol included in link:
\let\orighref\href
\renewcommand{\href}[2]{\orighref{#1}{#2\,\faExternalLink}}


\tolerance=1
\emergencystretch=\maxdimen
\hyphenpenalty=10000
\hbadness=10000

\usepackage{fontawesome}

\begin{document}

    \name{\Huge Denis Zakharov\\[20pt]} % the \\[12pt] adds a blank line after name

    \address{August 2023 \\ Saint Petersburg, Russia}

    \address{
        \faEnvelopeO \, \href{mailto:misterzurg@gmail.com}{misterzurg@gmail.com} \\
        \faGithub    \, \href{https://github.com/MisterZurg}{github.com/MisterZurg} \\
        \faLinkedinSquare  \, \href{linkedin.com/in/misterzurg/}{linkedin.com/in/misterzurg}
    }

    \begin{resume}
        \section{\uppercase{Working Experience} (3 years total)}

        \begin{spacing}{0.3}
            \textcolor[RGB]{220,220,220}{\rule{\linewidth}{0.4pt}}
        \end{spacing}

        \begin{tabular}{ll}
            May 2021 -- now \qquad \qquad & \textbf{\href{https://hyperskill.org}{Golang Track Author at Hyperskill}}, Go Content Team \\
            & Go, Algorithms, Data Structures, Math, DevOps \\
        \end{tabular}

        \begin{itemize} \itemsep -2pt
            \item Contribute to Introduction to Go track \href{https://hyperskill.org/tracks/25?category=12}{with 7k+ students}
            \item \href{https://hyperskill.org/tracks/43?category=20}{Working on Go Developer track} that deep dive into advanced programming concepts Software construction, SQL and Databases, Packages and modules, Programming concepts, OOP, Concurrency etc.

            \item Created more than 60 coding and comprehension problems for practicing learned theory.
        \end{itemize}

        \begin{tabular}{ll}
            Jul 2021 -- Jan 2022 \quad & \textbf{\href{https://ozon.tech/}{SE Intern at Ozon Tech}}, Autosorters Infrastructure Team \\
            & Go, Postgre, Kubernetes, Graylog, Grafana, Prometheus, Jaeger, Vault \\
        \end{tabular}

        \begin{itemize} \itemsep -2pt
            \item Developed barcode parse logic that reduced number of alerts by 30\%
            \item Build a team-space Grafana dashboard that covers all projects performance.
            \item Create a alert chat, that tags maintainer if there is need to be fixed.  
            \item Maintained projects by reacting on alerts, keeping them up to date adding metrics and filling with testcases.
        \end{itemize}

        See full list of my working experience on my \href{linkedin.com/in/misterzurg/}{Linkedin profile}.


        \section{\uppercase{Personal Projects}}
        \begin{spacing}{0.3}
            \textcolor[RGB]{220,220,220}{\rule{\linewidth}{0.4pt}}
        \end{spacing}
        \textbf{\href{https://github.com/MisterZurg/edu_tinkoff_Backend-Academy-2023/tree/dungeon-master/Go-laguage-part}{Smart Home modeling}} (Go)~--- application that implements the functions of a smart home hub a divice that controls all other devices in the smart house like sensors, switch, lamps sockets and a clocks.
        
        \textbf{\href{https://github.com/MisterZurg/academy_yandex_Backend-School-2023/tree/master/product}{Yandex Lavka}} (Go, Echo, Postgre, Docker, Goose, Rate Limit)~--- REST API application that performs distribution of orders to couriers like in real Yandex Lavka.
        
        \textbf{\href{https://github.com/MisterZurg/stepik_VK_Hadoop}{Hadoop Stepik}} (Go, MapReduce)~--- usage of the MapReduce program model for BigData using Hadoop via Hadoop Streaming for storing and processing from the Hadoop course.
        
         \textbf{\href{https://marketplace.visualstudio.com/items?itemName=misterzurg.acsl-ansi-iso-c-specification-language}{ACSL VS Code Support}} (JS, RegExp)~--- ANSI/ISO C Specification Language (ACSL) support for Visual Studio Code within Language Server Extension and Oniguruma RegExps.

        \section{\uppercase{Education}}
        \begin{spacing}{0.3}
            \textcolor[RGB]{220,220,220}{\rule{\linewidth}{0.4pt}}
        \end{spacing}
%\renewcommand{\arraystretch}{1.4}
        \begin{tabular}[t]{l l}
            2022 -- now & \textbf{Master of Computer Science}, GPA $4.7/5.0$\\
            & ITMO University \\
            2018 -- 2022 & \textbf{Bachelor of Computer Science}, GPA $4.9/5.0$  \\
            & Saint-Petersburg State University of Telecommunications                                                                                                              \\
            2021 -- now & \makecell[l]{\textbf{\href{hhttps://www.coursera.org/ucsd}{US SanDiego, Coursera}}, \\
            \href{https://www.coursera.org/specializations/data-structures-algorithms}{Data Structures and Algorithms Specialization}}
        \end{tabular}

        % \section{\uppercase{Skills}}
        % \begin{spacing}{0.3}
        %     \textcolor[RGB]{220,220,220}{\rule{\linewidth}{0.4pt}}
        % \end{spacing}
        % Python $\cdot$ Kotlin $\cdot$ C++ $\cdot$ Git $\cdot$ Algorithms $\cdot$ Data Structures $\cdot$ SQL $\cdot$ Linux $\cdot$ System Programming $\cdot$ Data Analysis $\cdot$ Image Analysis $\cdot$ Linguistics $\cdot$ Conferences (organizer, speaker, listener)


        % \textbf{Languages:} English fluent, Russian native

    \end{resume}
\end{document}
